The impact of cosmic variance on constraining the mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z \sim 3$

### 2014-04-03 paper/ms.tex
conclusions

We then proceed with a thorough exploration of the space of free
parameters $M_{\rm min}, M_{\rm max}$ and $f_{\rm occ}$ describing the
model. We look for consistency with two observational constraints: the
surface number density distribution and the angular correlation
function. Out of the initial $9000$  combinations of parameters in the
model we find $40$ combination of parameters consistent with
observations.

@@

The wide range of occupation fraction values is unexpected from
previous studies \citep[i.e.][]{Gawiser2007,Ouchi2010}  that
unanimously favor low values on the range of $10^{-2}$. Nevertheless,
all the halo mass ranges deduced in previous analysis are a subset of
the models we find in this paper, all of the best models support the
notion that the most massive halos at $z=3.1$ do not host detectable
LAEs.

  From the point of view of Dark Energy surveys such as the Hobby-Eberly
  Telescope Dark Enery Experiment (HETDEX) the
  narrow mass range for LAEs can be seen as an advantage because its
  simplicity in their modeling aiming at recovering cosmological
  parameters We foresee that the observations with new instruments
(such as the Multi Unit Spectroscopic Explorer (MUSE), Hyper
SuprimeCam and HETDEX) covering larger fields and a wider range of
luminosities will be key in reducing cosmic variance and imposing
tighter constraints on the properties of dark matter halos hosting
LAEs.

Finally, additional modeling for \ly radiation transfer is needed to
put tighter constraints on  occupation fraction in high redshift
halos, also paying attention to other physical phenomena, such as the
stochasticity \citep{ForeroRomero2013} in the star formation process,
which might play a role in introducting detection biases in high redshift
LAEs.

>>>>

We proceeded with a thorough exploration of the space of 
parameters ($M_{\rm min}$, $M_{\rm max}$, $f_{\rm occ}$) describing the
model. We look for consistency with two observational constraints: the
surface number density distribution and the angular correlation
function. Out of the initial $9000$  combinations of parameters in the
model we find $40$ combination of parameters consistent with
observations.

@@

The wide range of occupation fraction values is unexpected from
previous studies \citep[i.e.][]{Gawiser2007,Ouchi2010}  that
unanimously favor low values on the range of $10^{-2}$ and only
consider values of $0.1$ as an upper limit. Nevertheless, all the halo
mass ranges deduced in previous analysis are a subset of the models we
find in this paper. All our the best models support the notion that the
most massive halos at $z=3.1$ do not host detectable LAEs.

Additional modeling for \ly radiation transfer is needed to
put tighter constraints on  occupation fraction in high redshift
halos, also paying attention to other physical phenomena, such as the
stochasticity \citep{ForeroRomero2013} in the star formation process,
which might play a role in introducing detection biases in high redshift
LAEs.

From the point of view of Dark Energy surveys such as the Hobby-Eberly
Telescope Dark Enery Experiment (HETDEX) the narrow mass range for
LAEs can be seen as an advantage because its simplicity in their
modeling aiming at recovering cosmological parameters. We foresee that
the observations with new instruments (such as the Multi Unit
Spectroscopic Explorer (MUSE), Hyper SuprimeCam and HETDEX) covering
more fields and a wider range of luminosities will be key in fully
understanding the effects of cosmic variance  and imposing tighter
constraints on the properties of dark matter halos hosting LAEs.
